Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
Updated

This mixed scheme avoids the problem of multiple explorations from the
same  cell.  This  is  done by  maintaining  a flag  in  each cell  to
indicate whether it was copied using reachability.

\subsection{Garbage collection for references on print stack}
In lazy  languages the evaluation of  closures is driven  by the print
function~\cite{Jones87}.  Printing of  atomic values is
simple  and  does  not  trigger  a garbage  collection.   In  case  of
\CONS\ cells, the \CAR\ is first  printed followed by \CDR.  In a lazy
language, both \CAR\ and \CDR\ could be closures requiring evaluation,
and this  may trigger  a garbage collection.   When this  happens.  we
have to consider  any references that might be on  the print stack and
copy them. We extend the liveness analysis to the print function and
use its results during garbage collection.

>>>>

Another advnatage of  this mixed garbage collection scheme  is that it
avoids the problem of multiple  explorations from the same cell.  This
is done by maintaining a flag in  each cell to indicate whether it was
copied using reachability.

\subsection{Garbage collection for references on print stack}
In lazy  languages the evaluation of  closures is driven  by the print
function~\cite{Jones87}.  Printing of  atomic values is
simple  and  does  not  trigger  a garbage  collection.   In  case  of
\CONS\ cells, the \CAR\ is first  printed followed by \CDR.  In a lazy
language, both \CAR\ and \CDR\ could be closures requiring evaluation,
and this  may trigger  a garbage collection.   When this  happens.  we
have to consider  any references that might be on  the print stack and
copy them. We extend the liveness analysis to the print function and
use its result during garbage collection.
